A simple probabilistic approach to finding strongly lensed quasars in ground-based imaging

### 2013-01-29 docs/paper1.tex
psfig cleaned out
affils
Working on step sizes in lens model

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}

% Macros:
\input{macros.tex}
\input{addresses.tex}
\newcommand\nodata{ ~$\cdots$~ }%

@@

\title[finding lensed quasars]{A simple probabilistic approach to finding strongly lensed quasars in ground-based imaging}

\author[]{%
  Philip J. Marshall$^{1,2}$\thanks{\pjmemail},
  David W. Hogg$^{3}$,
  Dustin Lang$^{4}$,
  Eric P. Morganson$^{5}$ 
  \medskip\\
  $^1$\oxford\\
  $^2$\kipac\\
  $^3$\nyu\\
  $^4$\cmu\\
  $^5$\mpia
}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Packages:
% \input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}

% Macros:
\input{macros.tex}
\input{addresses.tex}

@@

\title[Finding lensed quasars]
{A simple probabilistic approach to finding 
strongly lensed quasars in ground-based imaging}

\author[]{%
  Philip J. Marshall$^{1,2}$\thanks{\pjmemail},
  David W. Hogg$^{3,4}$,
  Dustin Lang$^{5}$,
  Eric P. Morganson$^{4}$ 
  \medskip\\
  $^1$\oxford\\
  $^2$\kipac\\
  $^3$\nyu\\
  $^4$\mpia\\
  $^5$\cmu
}

@@

Our main goals can be summarised as follows:

\item We don't understand this.

\item Nor that.

One thing we know for sure is that the MNRAS style file deals badly
with ``enumerate'' blocks.

@@

% do these comment headers really help?
% after all, the \section{} commands say THE SAME THING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
